\documentclass[article]{aaltoseries}
\usepackage[utf8]{inputenc}


\begin{document}
 
%=========================================================

\title{Survey of Mobility prediction mechanisms in vehicular networks}

\author{Sankar Bhagavatheesvaran Subramani% Your first and last name: do _not_ add your student number
\\\textnormal{\texttt{sankar.bhagavatheesvaransubramani@aalto.fi}}} % Your Aalto e-mail address

\affiliation{\textbf{Tutor}: Özgür Akgül} % First and last name of your tutor

\maketitle

%==========================================================

\begin{abstract}
The fast-paced development of self-driving technologies have brought about the need for development of accompanying technologies which can greatly benefit such as Intelligent Traffic Management, Safety and Comfort. \newline
These services cannot be realized without knowledge of the location of the vehicles. \newline
This has led to rise of smart systems which predict the volume of vehicles in an given area,while enduring privacy. Machine learning & Artificial Intelligence form a crucial basis of such systems.\newline
Processing is not relegated to just the fixed infrastructure but also on the vehicles themselves. This leads to additional challenge of managing of temporary mobile processing resources on the vehicles.Hence, dynamic parameters such as duration the vehicle is expected to an area of interest, speed of the vehicle have a bearing on the system performance.\newline
  Thus Mobility prediction is a crucial exercise in resource management, architectural fit machine learning techniques and foremost concerns which are reliability and privacy. 
 This paper is a survey of these solutions and compares them in terms of features, quality of prediction, and technologies involved.

  

\vspace{3mm}
\noindent KEYWORDS:
Mobility Prediction,Self-Driving,AI,Machine Learning
\end{abstract}


%============================================================




%------------------------------------------------------------




%------------------------------------------------------------






%------------------------------------------------------------





%============================================================







%------------------------------------------------------------




%------------------------------------------------------------







%------------------------------------------------------------







%============================================================




%============================================================




\end{document}
